Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-05-31 schemes.tex
Editing RLNC decoding. Need to finish the recoding part

For indicating a receiver which of the original packets were utilized
to create a coded packet, a simple and useful choice is to append
its coding coefficients as a header of the coded packet. Hence, an
amount of overhead is included in every coded packet given that we
need to provide some signalling needed for decoding. The coding
coefficients overhead amount for packet $i$, $|v_i|$, can be quantified
as:
%
\begin{align} \label{eq:coded_packet_coef}
|v_i| &= \sum_{j=1}^{g} |v_{i,j}| = g \times \lceil \log_{2} (q)
\rceil ~ [\mathrm{bits}]
\end{align}

\subsubsection{Decoding}
To be able to decode a batch of $g$ packets, a \ac{l.i.} set of $g$
coded packets, $C_i,\ i \in [1,g]$ is required in order to get the
original information. Once this set has been collected for any receiver,
the original packets can be found by computing the solution of a system
of linear equation using \ac{GF} aritmethics. Thus, we define
$\textbf{C} = \left[C_1 \ldots C_g \right]^T$ and
$\textbf{P} = \left[P_1 \ldots P_g \right]^T$. Algebraically, decoding
simplifies to finding the inverse of $\textbf{V}$ in the linear system
$\textbf{C} = \textbf{V} \cdot \textbf{P}$, which can achieved using
Gaussian elimination techniques \cite{fragouli2006network} that can
be efficient. For decoding to be possible, the (coding) matrix $\textbf{V}$
must contain any set of $g$ linearly independent packets $C_i$ in order
to reduce to row-echelon form. The coding matrix is represented as follows:
%
\begin{align} \label{eq:coding_matrix}
\textbf{V} =
\left[
\begin{array}{c}
        v_1    \\ \hline
        \vdots \\ \hline
        v_g    \\
\end{array}
\right]
=
\left[
\begin{array}{ccc}
        v_{1,1} & \ldots & v_{1,g} \\
        \vdots  & \ddots & \vdots  \\
        v_{g,1} & \ldots & v_{g,g} \\
\end{array}
\right]
\end{align}
%
The decoder begins to compute and remove the contributions from each
of the pivot elements, e.g. leftmost elements in the main diagonal of
\eqref{eq:coding_matrix}, to reduce $\textbf{V}$ to reduced echelon
form. In this way, it is possible to recover the original set of packets.

\subsubsection{Recoding}
Network coding allows intermediate nodes in a network to
recombine (or recode) packets from their sources whether they are
coded or not. In general, a recoded packet should be indistinguishable
from a coded one. Thus, we define a recoded packet as
$R_i$ and its corresponding encoding vector as
$w_i$ with coding coefficients $ \left[w_{i,1} \ldots w_{i,g} \right]$,
as follows:
%
\begin{align}
\label{eq:recoded_packet}
R_i = \bigoplus_{j=1}^{g} w_{i,j} \otimes C_j  ,\ \forall i \in [1,g]
\end{align}

@@

\begin{align} \label{eq:sparse_coded_packet}
    %C_i  &= \bigoplus_{j=1}^{g} \text{B}(d)_{j} \, v_{i,j} \otimes P_j ,\ \forall i \in [1,g] ,\
    C_i  &= \bigoplus_{j=1}^{g} \text{B}(d) \, v_{i,j} \otimes P_j ,\ \forall i \in [1,g] ,\
    v_{i,j} > 0,\
    d \in
    \begin{cases}
        {(0,0.5]} & \text{for } q=2 \\
        {(0,1]} & \text{for } q>2
    \end{cases}
\end{align}

>>>>

For indicating a receiver which packets were utilized
to create a coded one, a simple yet versatile choice is to append
its coding coefficients as a header of the coded packet. Hence, an
amount of overhead is included in every coded packet given that we
need to provide some signalling needed for decoding. The coding
coefficients overhead amount for packet $i$, $|v_i|$, can be quantified
as:
%
\begin{align} \label{eq:coded_packet_coef}
|v_i| &= \sum_{j=1}^{g} |v_{i,j}| = g \times \lceil \log_{2} (q)
\rceil ~ [\mathrm{bits}]
\end{align}

\subsubsection{Decoding}
To be able to decode a batch of $g$ packets, a \ac{l.i.} set of $g$
coded packets, $C_i,\ i \in [1,g]$ is required at a decoder.
Once this set has been collected for a decoder,
the original packets can be found by computing the solution of a system
of linear equations using \ac{GF} aritmethics. Thus, we define
$\textbf{C} = \left[C_1 \ldots C_g \right]^T$ and
$\textbf{P} = \left[P_1 \ldots P_g \right]^T$. Algebraically, decoding
simplifies to finding the inverse of $\textbf{V}$ in the linear system
$\textbf{C} = \textbf{V} \cdot \textbf{P}$, which can achieved using
efficient Gaussian elimination techniques \cite{fragouli2006network}.
On real applications, decoding is performed on-the-fly, e.g. the pivots are
computed as packets are progressively received, in order to minimize the computation
delay for each step. The coding matrix is represented as follows:
%
\begin{align} \label{eq:coding_matrix}
\textbf{V} =
\left[
\begin{array}{c}
        v_1    \\ \hline
        \vdots \\ \hline
        v_g    \\
\end{array}
\right]
=
\left[
\begin{array}{ccc}
        v_{1,1} & \ldots & v_{1,g} \\
        \vdots  & \ddots & \vdots  \\
        v_{g,1} & \ldots & v_{g,g} \\
\end{array}
\right]
\end{align}
%
A decoder starts to calculate and substract contributions from each
of the pivot elements, e.g. leftmost elements in the main diagonal of
\eqref{eq:coding_matrix}, from top to bottom. The purpose is to obtain 
the equivalence  $\textbf{V}$ in its reduced echelon form. The steps
for reducing the matrix by elementary row operations are carried each
a \ac{l.i.} packet is received. Once in reduced echelon form, packets
can be retrieved by doing a substitution starting from the lastest
coded packet. In this way, the amount of elementary operations at the end
is diminished.

\subsubsection{Recoding}
An inherent property of \ac{NC} is the possibility for intermediate nodes
in a network between a source and a destination, to create coded packets
even from coded packets sent from the source. In general, a recoded packet should be indistinguishable
from a coded one. Thus, we define a recoded packet as
$R_i$ and its corresponding encoding vector as
$w_i$ with coding coefficients $ \left[w_{i,1} \ldots w_{i,g} \right]$,
as follows:
%
\begin{align}
\label{eq:recoded_packet}
R_i = \bigoplus_{j=1}^{g} w_{i,j} \otimes C_j  ,\ \forall i \in [1,\ldots)
\end{align}

@@

\begin{align} \label{eq:sparse_coded_packet}
    %C_i  &= \bigoplus_{j=1}^{g} \text{B}(d)_{j} \, v_{i,j} \otimes P_j ,\ \forall i \in [1,g] ,\
    C_i  &= \bigoplus_{j=1}^{g} \text{B}(d) \, v_{i,j} \otimes P_j ,\ \forall i \in [1,g] ,\
    v_{i,j} > 0,\
    d \in
    \begin{cases}
        {(0,0.5]} & \text{for} q = 2 \\
        {(0,1]} & \text{for} q > 2
    \end{cases}
\end{align}
